Trafficking synaptic cargo in complex morphologies involves tradeoffs in speed and precision

### 2015-09-02 latex/paper.tex
new intro paragraph

Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
In order to maintain appropriate connectivity, or to alter it as a means of encoding memories, numerous enzymes and macromolecules need to be transported along dendrites to the synapses that need them.
How is this logistical problem solved at the subcellular level? And how might a biologically plausible solution constrain the behavior of synaptic plasticity `rules' and learning in general?

Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion [REFS].
The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \cite{Mironov_2007,Wang_2009}.
It is therefore conceivable that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo trigger its release from the motor protein complexes as they pass.
This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.

>>>>

Neurons often have complex dendritic trees, reflecting the dense and structured synaptic connectivity that supports nervous system function.
In order to maintain appropriate connectivity, or to alter it in response to external events, numerous enzymes and macromolecules must be repeatedly replenished and distributed amongst a staggering number of synaptic contacts.
A human might draw inspiration from FedEx to design a solution based on transport hubs and an addressing system.
However, it is unclear how such a sophisticated scheme could be implemented on a microscopic scale in a flexible and robust manner.
Futhermore, other biological transport systems (e.g. in ant colonies; \cite{Deneubourg_1990}) utilize more decentralized strategies based on simple local cues and decisions.
Is it possible to achieve reliable transport in dendrites without an addressing system?
What are the limitations and potential advantages of a decentralized transport system, and how might these constrain the behavior of synaptic plasticity `rules' and, by extension, circuit connectivity?

Transport along dendrites is mediated by motor proteins (kinesins and dyneins) that walk along microtubules, carrying cargo at a rate that far exceeds passive diffusion [REFS].
The mechanisms that detach and sequester cargo at specific places in dendrites are not fully understood, but are known to depend on local biochemical signals that can be influenced by synaptic activity, such as transient elevations in cyclic AMP or $[Ca^{2+}]$ \citep{Mironov_2007,Wang_2009}.
It is therefore conceivable that synaptic cargo transport is controlled in a distributed fashion, in which synapses that require cargo trigger its release from the motor protein complexes as they pass.
This idea is a variant of the well-known synaptic tagging hypothesis \citep{Frey_1997}, which proposes that synapses produce a biochemical `tag' that signals a requirement for synaptic building blocks as part of the plasticity process.
